---
title: iSOCIALISE - Investigating SOcial Competence and Isolation in children with Autism taking part in Lego®-based therapy clubs In School Environments
output:
  html_document:
    toc: true
    toc_depth: 3
bibliography: sections/bibliography.bib
---

```{r setup, echo = FALSE, warning = FALSE, message = FALSE, results = 'hide', cache = FALSE, eval = TRUE}
library(lme4)
library(influence.ME)
library(sjPlot)
##opts_chunk$set(dev = 'pdf')
opts_chunk$set(cache.path = 'cache/',
               width    = 200,
               fig.height = 8,
               fig.width  = 8,
               warning = FALSE,
               message = FALSE)
options(digits = 3)
## Ensure anchors are assessed first
## opts_knit$set(eval.after = 'echo')
## Hooks
## knit_hooks$set(anchor = hook_anchor)
## Set a seed
set.seed(69027181)
## Set sensible defaults
ggplot2.opts <- list()
ggplot2.opts$binwidth <- 30
## sjPlot defaults
## sjPlot::theme_sjplot(base.theme = theme_bw())
## Exclusions
##
## The following 'non-recruited' need excluding from all analyses
## exclusions <- c()

## Set the study name and procotol versions
study <- list()
study$name             <- 'iSOCIALISE'
study$protocol_version <- 'v3 2017-11-21'
```

```{r backup, echo = FALSE, eval = TRUE}
## Make a backup of current output based on time stamp by obtaining the
## modified time of the existing file and constructing a command to
## copy this to the sub-directory 'arch/' modifying the filename to include
## the timestamp.  This is done on a daily basis (otherwise './arch/'
## directory can become very large!)
##
## Get the current date
mtime <- file.info('isocalise_sap.docx')$mtime %>% as.Date()
## Remove existing archives  from today
cmd <- paste0('rm arch/isocalise_sap-', mtime, '.docx.bz2')
system(cmd)
## Copy the existing .docx to arch, adding todays date and compress
cmd <- paste0('cp isocalise_sap.docx arch/isocalise_sap-', mtime, '.docx && bzip2 arch/isocalise_sap-', mtime, '.docx')
system(cmd)
## Get the current date
mtime <- file.info('isocalise_sap.html')$mtime %>% as.Date()
## Remove existing archives  from today
cmd <- paste0('rm arch/isocalise_sap-', mtime, '.html.bz2')
system(cmd)
## Copy the existing .html to arch, adding todays date and compress
cmd <- paste0('cp isocalise_sap.html arch/isocalise_sap-', mtime, '.html && bzip2 arch/isocalise_sap-', mtime, '.html')
system(cmd)

```
**ToDO** Create a frontispiece.



<!--- Page Break? --->
-----

# Summary
```{r child = 'sections/summary.Rmd', eval = TRUE}
```

# Introduction, study design and key objectives <!-- {.tabset .tabset-fade .tabset-pills} -->
```{r child = 'sections/overview.Rmd', eval = TRUE}
```

# Outcome Measures <!-- {.tabset .tabset-fade .tabset-pills} -->
```{r child = 'sections/outcome_measures.Rmd', eval = TRUE}
```

# Sample Size <!-- {.tabset .tabset-fade .tabset-pills} -->
```{r child = 'sections/sample_size.Rmd', eval = TRUE}
```

# Randomisation and Blinding <!-- {.tabset .tabset-fade .tabset-pills} -->
```{r child = 'sections/randomisation_blinding.Rmd', eval = TRUE}
```

# Interim Analyses and Data Monitoring Committees <!-- {.tabset .tabset-fade .tabset-pills} -->
```{r child = 'sections/interim_analyses.Rmd', eval = TRUE}
```

# Data Sources, data evaluability and analysis populations <!-- {.tabset .tabset-fade .tabset-pills} -->
```{r child = 'sections/data_sources.Rmd', eval = TRUE}
```

# Outline of Analyses <!-- {.tabset .tabset-fade .tabset-pills} -->
```{r child = 'sections/outline.Rmd', eval = TRUE}
```

# Detailed statistical methods and calculations <!-- {.tabset .tabset-fade .tabset-pills} -->
```{r child = 'sections/detailed_statistical_methods.Rmd', eval = TRUE}
```

# Data manipulation and definitions <!-- {.tabset .tabset-fade .tabset-pills} -->
```{r child = 'sections/data_manipulations.Rmd', eval = TRUE}
```

# Implementation <!-- {.tabset .tabset-fade .tabset-pills} -->
```{r child = 'sections/implementation.Rmd', eval = TRUE}
```

# Appendix   <!-- {.tabset .tabset-fade .tabset-pills} -->
```{r child = 'sections/appendix.Rmd', eval = TRUE}
```

# References

<!-- # References -->
