Sample output from running an example from `?glmer` are shown below along with various fixed and random effects plots followed by a plot of model assumptions.

**ToDo** Establish which diagnostic plots are of interest, some examples below, more are possible, I could plot them all, but would like to discuss which are preferred.

```{r glmer-example, echo = TRUE, warning = FALSE, message = FALSE, results = 'show', cache = FALSE, fig_width = 10, fig_height = 10, eval = TRUE}
## Run a dummy glmer model on sample data to demonstrate the structure of output
model1 <- glmer(cbind(incidence, size - incidence) ~ period + (1 | herd),
                cbpp, binomial, nAGQ = 0)
model1 %>% summary()

```

**Random Effects**
```{r glmer-example-random-effects, echo = FALSE, warning = FALSE, message = FALSE, results = 'hide', cache = FALSE, fig_width = 10, fig_height = 10, eval = TRUE}
## Diagnostic plots (see http://www.strengejacke.de/sjPlot/sjp.glmer/)
sjp.setTheme(base = theme_bw())
## Random Effects
sjp.glmer(model1, type = 're')
```

**Random Effects Quantile Plot**
```{r glmer-example-random-effects-qq, echo = FALSE, warning = FALSE, message = FALSE, results = 'hide', cache = FALSE, fig_width = 10, fig_height = 10, eval = TRUE}
## Quantile Plots for Random Effects
sjp.glmer(model1, type = 're.qq')
```

**Fixed Effects**
```{r glmer-example-fixed-effects, echo = FALSE, warning = FALSE, message = FALSE, results = 'hide', cache = FALSE, fig_width = 10, fig_height = 10, eval = TRUE}
## Fixed Effects
sjp.glmer(model1, type = 'fe')

```
**Fitted Values**
```{r glmer-example-fixed-fitted, echo = FALSE, warning = FALSE, message = FALSE, results = 'hide', cache = FALSE, fig_width = 10, fig_height = 10, eval = TRUE}
## Fixed Effects
## Extract data and predicted values, binding into a dataframe for plotting
model1_fitted <- data.frame(model1@frame, fitted_re = fitted(model1))
names(model1_fitted) <- c('Incidence', 'Period', 'Herd', 'Fitted')
model1_fixed <- fixef(model1) %>% data.frame()
ggplot(model1_fitted, aes(x      = Period,
                          y      = Fitted,
                          colour = Herd)) +
    geom_point() +
    geom_abline(intercept = model1_fixed[1,1],
                slope     = model1_fixed[2,1]) +
    geom_abline(intercept = model1_fixed[1,1],
                slope     = model1_fixed[3,1]) +
    geom_abline(intercept = model1_fixed[1,1],
                slope     = model1_fixed[4,1])  +
    theme_bw()



```

**Residuals v Fitted**
```{r glmer-example-fixed-residual-fitted, echo = FALSE, warning = FALSE, message = FALSE, results = 'hide', cache = FALSE, fig_width = 10, fig_height = 10, eval = TRUE}
model1_residual_fitted <- data.frame(Fitted    = fitted(model1),
                                     Residuals = residuals(model1))
ggplot(model1_residual_fitted,
       aes(x = Fitted,
           y = Residuals)) +
    geom_point() +
    theme_bw()

```

**ToDo** Are Standardise residuals and Fitted values for a true Q-Q Plot desirable?

**Model Assumptions**
```{r glmer-example-model-assumptions, echo = FALSE, warning = FALSE, message = FALSE, results = 'hide', cache = FALSE, fig_width = 10, fig_height = 10, eval = TRUE}
## Model Assumptions
sjp.glmer(model1, type = 'ma')


```

**Cooks Distance**
```{r glmer-example-model-leverage, echo = FALSE, warning = FALSE, message = FALSE, results = 'hide', cache = FALSE, fig_width = 10, fig_height = 10, eval = TRUE}
## Leverage and Cooks Distance using influence.ME
model1_influence <- influence(model1, obs = TRUE)
plot(model1_influence, which = 'cook')
cooks.distance(model1_influence)

```
