#### Sample Likert Plots

Likert Plots are a form of horizontal stacked bar charts that allow the visualisation of responses to questionnaires with categorical fields and will be used to visually display the responses for questionnaires used in this study.  Examples are shown below.


```{r example-likert, echo = FALSE, warning = FALSE, message = FALSE, results = 'hide', cache = FALSE, fig_width = 10, fig_height = 10, eval = TRUE}
dummy <- cbind(ifelse(runif(n =  240) > 0.5,
                      yes = 'Standard Care',
                      no  = 'Intervention'),
               runif(n =  240),
               runif(n =  240),
               runif(n =  240),
               runif(n =  240),
               runif(n =  240)) %>%
    as.tibble() %>%
    mutate(id = row_number())
names(dummy) <- c('Status', 'random1', 'random2', 'random3', 'random4', 'random5', 'id')
dummy <- mutate(dummy,
                Mobility = case_when(random1 >= 0    & random1 <= 0.14 ~ 'None',
                                     random1 >  0.14 & random1 <= 0.29 ~ 'Slight',
                                     random1 >  0.29 & random1 <= 0.46 ~ 'Moderate',
                                     random1 >  0.46 & random1 <= 0.64 ~ 'Severe',
                                     random1 >  0.64 & random1 <= 1.0  ~ 'Extreme'),
                `Self Care` = case_when(random2 >= 0    & random2 <= 0.26 ~ 'None',
                                        random2 >  0.26 & random2 <= 0.38 ~ 'Slight',
                                        random2 >  0.38 & random2 <= 0.56 ~ 'Moderate',
                                        random2 >  0.56 & random2 <= 0.74 ~ 'Severe',
                                        random2 >  0.74 & random2 <= 1.0  ~ 'Extreme'),
                `Usual Activity` = case_when(random3 >= 0    & random3 <= 0.20 ~ 'None',
                                             random3 >  0.20 & random3 <= 0.40 ~ 'Slight',
                                             random3 >  0.40 & random3 <= 0.60 ~ 'Moderate',
                                             random3 >  0.60 & random3 <= 0.80 ~ 'Severe',
                                             random3 >  0.80 & random3 <= 1.0  ~ 'Extreme'),
                `Pain` = case_when(random4 >= 0    & random4 <= 0.22 ~ 'None',
                                   random4 >  0.22 & random4 <= 0.39 ~ 'Slight',
                                   random4 >  0.39 & random4 <= 0.64 ~ 'Moderate',
                                   random4 >  0.64 & random4 <= 0.75 ~ 'Severe',
                                   random4 >  0.75 & random4 <= 1.0  ~ 'Extreme'),
                `Anxiety` = case_when(random5 >= 0    & random5 <= 0.19 ~ 'None',
                                      random5 >  0.19 & random5 <= 0.49 ~ 'Slight',
                                      random5 >  0.49 & random5 <= 0.58 ~ 'Moderate',
                                      random5 >  0.58 & random5 <= 0.75 ~ 'Severe',
                                      random5 >  0.75 & random5 <= 1.0  ~ 'Extreme')) %>%
    dplyr::select(-random1, -random2, -random3, -random4, -random5) %>%
    gather(Dimension, Response, -id, -Status)
ggplot(dummy, aes(Status, fill = Response)) +
    geom_bar(position = 'fill') +
    coord_flip() +
    xlab('') +
    ylab('Proportion') +
    facet_wrap(~Dimension, ncol = 1) +
    ggtitle('Likert Plot for EQ5D Responses') +
    theme_bw()
## Add percentages using solution at https://stackoverflow.com/a/25620672/1444043
##    stat_bin(aes(label = scales::percent((..count..) / sum(..count..))))


```

An alternative method of plotting these is shown below.  It uses a different method to organise the data and then plot it using the `sjPlot::sjp.stackfrq()` function from  the [sjPlot](https://CRAN.R-project.org/package=sjPlot) package) and makes it easy to overlay the percentages within each grouping (possible with the above, but considerably more work).

```{r example-likert-sjplot, echo = FALSE, warning = FALSE, message = FALSE, results = 'hide', cache = FALSE, fig_width = 10, fig_height = 10, eval = TRUE}
set_theme(base = theme_bw())
dplyr::filter(dummy, Status == 'Standard Care') %>%
    dplyr::select(-Status)  %>%
        spread(Dimension, Response) %>%
        dplyr::select(-id) %>%
        sjp.stackfrq(title = 'Standard Care')
dplyr::filter(dummy, Status == 'Intervention') %>%
    dplyr::select(-Status)  %>%
        spread(Dimension, Response) %>% head()
        dplyr::select(-id) %>%
        sjp.stackfrq(title = 'Intervention')
rm(standard, intervention)
## dplyr::filter(dummy, Dimension == 'Mobility') %>%
##     dplyr::select(-Dimension)  %>%
##         spread(Status, Response) %>%
##         dplyr::select(-id) %>%
##         sjp.stackfrq(title = 'Mobility')

```
