**TODO** Awaiting details of schools that have expressed an interest in participation.


Each block had a total of `r n` allocations generated in blocks of size `r block_sizes` for two possible levels (`Standard Care` and `LEGO Therapy`).  This was repeated four times over for the four possible stratum formed from the two two-level stratification variables (`Primary` v's `Secondary` school type and `<= 3` v's `> 3` eligible participants).


```{r results_schedule_plot, cache = FALSE, echo = FALSE, warnings = FALSE, results = 'hide', eval = TRUE}
## Plot the distribution of randomisation by stratum
ggplot(randomisation,
        aes(x    = stratum,
            fill = treatment)) +
    geom_histogram(stat     = "count",
                   position = "dodge") +
    xlab('Stratum') +
    ylab('Number allocated') +
    labs(fill = 'Treatment Allocation') +
    theme_bw()

```


The full randomisation schedule is printed below for reference and has been uploaded to a Google Sheet for use by study managers in randomising schools and data management and statistics in analysis.

```{r results_schedule_full, cache = FALSE, echo = FALSE, warnings = FALSE, results = 'show', eval = TRUE}
randomisation %>%
    kable(caption = 'Full Randomisation schedule by Strata',
          colnames = c('Site ID', 'Stratum', 'Block ID', 'Block Size', 'Treatment Allocation'))

```
