Each block had a total of `r n` allocations generated in blocks of size `r block_sizes` for two possible levels (`Standard Care` and `LEGO Therapy`), although because of the underlying way in which block sizes are randomised there is the possibility tha the total number of allocations within a stratum may exceed `r n`.  This was repeated four times over for the four possible stratum formed from the two two-level stratification variables (`Primary` v's `Secondary` school type and `<= 3` v's `> 3` eligible participants).


```{r results_schedule_plot, cache = FALSE, echo = FALSE, warnings = FALSE, results = 'hide', eval = TRUE}
## Plot the distribution of randomisation by stratum
ggplot(randomisation,
        aes(x    = stratum,
            fill = treatment)) +
    geom_histogram(stat     = "count",
                   position = "dodge") +
    xlab('Stratum') +
    ylab('Number allocated') +
    labs(fill = 'Treatment Allocation') +
    theme_bw()

```


The full randomisation schedule is printed below for reference and has been uploaded to a [Google Sheet](https://docs.google.com/a/sheffield.ac.uk/spreadsheets/d/1FiaitHHY4lusGC64vxAtKYaOOIsUL6TLQafDin-gSNY/edit?usp=sharing) ([https://docs.google.com/a/sheffield.ac.uk/spreadsheets/d/1FiaitHHY4lusGC64vxAtKYaOOIsUL6TLQafDin-gSNY/edit?usp=sharing](https://docs.google.com/a/sheffield.ac.uk/spreadsheets/d/1FiaitHHY4lusGC64vxAtKYaOOIsUL6TLQafDin-gSNY/edit?usp=sharing)) for use by study managers in randomising schools and data management and statistics in analysis.  Please contact [Neil Shephard](mailto:n.shephard@sheffield.ac.uk) for permission to modify this document.

### Using the Randomisation Schedule

Using the randomisation schedule is straight-forward.  When a school is ready to be randomised look at the characteristics on which it is being stratified, i.e. Primary or Secondary and whether there are <6 or >= 6 consented participants.  Based on this go to the first row for the given stratum for which there is a blank allocation and enter the schools name and inform them of their allocation which is in the column `treatment`.  For example the first school to be randomised is a Secondary school with less than 6 consented participants, this stratum begins on row 102 of the spreadsheet and allocates the school to `Standard Care`.  If the second school for randomisation is a Primary School with >= 6 consented participants the stratum begins on row 52 and allocates the school to `Standard Care`.  If the third school is also a Primary School with >= 6 consented participants the next allocation within this stratum is on row 53 and allocates the school to `LEGO Therapy`.  Repeat for each school that needs randomising.


```{r results_schedule_full, cache = FALSE, echo = FALSE, warnings = FALSE, results = 'show', eval = TRUE}
randomisation %>%
    kable(caption = 'Full Randomisation schedule by Strata',
          col.names = c('Site ID', 'Stratum', 'Block ID', 'Block Size', 'Treatment Allocation'))

```

```{r results_schedule_upload, cache = FALSE, echo = FALSE, warnings = FALSE, results = 'hide', eval = TRUE}
## Write the randomisation file to CSV and upload to GoogleSheets
## First add in an extra blank column for school name to be recorded in
randomisation$school <- ""
file <- '../data/randomisation.csv'
write.csv(randomisation,
          file = file,
          row.names = FALSE)
gs_upload(file = file,
          sheet_title = 'iSocialise Randomisation Schedule',
          overwrite   = TRUE)

```
